Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-08 ms.tex
table--headings still need adjustment
Fixing the MdotCompton to be consistent with new prescription.

\begin{table*}
\begin{threeparttable}
%\centering
\begin{minipage}{18cm}
\caption{Summary of Numerical Solutions}
\begin{tabular}{lccccccccc}
  \hline
  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.2}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.2}{\eta}\right)_{r_s}^{(d)}$}  \\
  ($M_{\odot}$) & (km s$^{-1}$) & (pc) &- & - & - &  & \\ 
\hline
 & & & Cusp Galaxies, $\Gamma^{(a)} = 0.8$ & & & & & \\
 $    10^{ 6 }$ & 300 & 0.8 & 100 & $ 6.4 \times 10^{ -5 }$ & 17 \\
... & 600 & 0.8 & 100 & $ 1.1 \times 10^{ -5 }$ & $ 1.6 \times 10^{ 3 }$ \\
... & 1200 & 0.8 & 100 & $ 1.9 \times 10^{ -6 }$ & $ 7.2 \times 10^{ 4 }$ \\
$    10^{ 7 }$ & 300 & 0.8 & 25 & $ 3.9 \times 10^{ -4 }$ & 1.8 \\
... & ... & 0.8 & 50 & $ 3.9 \times 10^{ -4 }$ & $\mathbf{0.82}$ \\
... & ... & 0.8 & 100 & $ 5.2 \times 10^{ -4 }$ & $\mathbf{0.33}$ \\
... & ... & 0.8 & 200 & $ 5.9 \times 10^{ -4 }$ & $\mathbf{0.18}$ \\
... & ... & 0.8 & 400 & $ 1.8 \times 10^{ -3 }$ & $\mathbf{ 1.9 \times 10^{ -2 }}$ \\
... & 600 & 0.8 & 25 & $ 3.6 \times 10^{ -5 }$ & $ 4.4 \times 10^{ 2 }$ \\
... & ... & 0.8 & 100 & $ 3.6 \times 10^{ -5 }$ & $ 4.4 \times 10^{ 2 }$ \\
... & 1200 & 0.8 & 100 & $ 6.4 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 4 }$ \\
$    10^{ 8 }$ & 300 & 0.8 & 25 & $ 9.4 \times 10^{ -4 }$ & $\mathbf{1}$ \\
... & ... & 0.8 & 50 & $ 1.6 \times 10^{ -3 }$ & $\mathbf{0.19}$ \\
... & ... & 0.8 & 100 & $ 3.3 \times 10^{ -3 }$ & $\mathbf{ 2.2 \times 10^{ -2 }}$ \\
... & ... & 0.8 & 200 & $ 7.2 \times 10^{ -3 }$ & $\mathbf{ 2.1 \times
  10^{ -3 }}$ \\
$    10^{ 8 }$ & 450 & 0.8 & 100 & $ 4.4 \times 10^{ -4 }$ & 4 \\
...$^{\dagger}$ & ... & 0.8 & 100 & $ 2.8 \times 10^{ -3 }$ & $\mathbf{2.8}$ \\
... & 600 & 0.8 & 25 & $ 1.3 \times 10^{ -4 }$ & $ 1.1 \times 10^{ 2
}$ \\
... & ... & 0.8 & 100 & $ 1.5 \times 10^{ -4 }$ & 76 \\
...$^{\dagger}$ & ... & 0.8 & 100 & $ 1.5 \times 10^{ -4 }$ & 70 \\
... & ... & 0.8 & 200 & $ 1.5 \times 10^{ -4 }$ & 67 \\
... & ... & 0.8 & 400 & $ 1.6 \times 10^{ -4 }$ & 58 \\
... & 1200 & 0.8 & 100 & $ 2.0 \times 10^{ -5 }$ & $ 7.2 \times 10^{ 3 }$ \\
  \hline
 & & & Core Galaxies, $\Gamma = 0.1$ & & & & & & \\
$    10^{ 6 }$ & 600 & 0.1 & 25 & $ 8.2 \times 10^{ -6 }$ & 99 \\
... & ... & 0.1 & 50 & $ 8.5 \times 10^{ -5 }$ & $\mathbf{0.45}$ \\
... & 1200 & 0.1 & 25 & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
... & ... & 0.1 & 50 & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
... & ... & 0.1 & 100 & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
$    10^{ 7 }$ & 600 & 0.1 & 25 & $ 4.3 \times 10^{ -5 }$ & 41 \\
... & ... & 0.1 & 50 & $ 2.3 \times 10^{ -4 }$ & $\mathbf{0.38}$ \\
... & 1200 & 0.1 & 25 & $ 1.8 \times 10^{ -6 }$ & $ 2.2 \times 10^{ 4 }$ \\
... & ... & 0.1 & 50 & $ 2.0 \times 10^{ -6 }$ & $ 1.7 \times 10^{ 4 }$ \\
... & ... & 0.1 & 100 & $ 2.5 \times 10^{ -6 }$ & $ 9.8 \times 10^{ 3 }$ \\
$    10^{ 8 }$ & 600 & 0.1 & 25 & $ 1.1 \times 10^{ -4 }$ & 31 \\
... & ... & 0.1 & 50 & $ 3.0 \times 10^{ -4 }$ & 3 \\
... & ... & 0.1 & 100 & $ 4.0 \times 10^{ -3 }$ & $\mathbf{ 5.7 \times 10^{ -3 }}$ \\
... & 1200 & 0.1 & 25 & $ 8.4 \times 10^{ -6 }$ & $ 5.6 \times 10^{ 3 }$ \\
... & ... & 0.1 & 50 & $ 9.8 \times 10^{ -6 }$ & $ 4.0 \times 10^{ 3 }$ \\
... & ... & 0.1 & 100 & $ 1.2 \times 10^{ -5 }$ & $ 2.4 \times 10^{ 3 }$ \\
... & ... & 0.1 & 200 & $ 2.1 \times 10^{ -5 }$ & $ 6.5 \times 10^{ 2 }$ \\
... & ... & 0.1 & 400 & $ 6.2 \times 10^{ -3 }$ & $\mathbf{ 5.8 \times 10^{ -3 }}$ \\
  \hline

@@

If Compton heating acts alone, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then solving equation
(\ref{eq:vC}) for $\tilde{v}_{\rm w}$ yields
\begin{align} v_{w}^{\rm C} \simeq
  \begin{cases} 150 \eta_{0.02}^{0.21}T_{\rm
C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}
&, \text{core}\\ 96 \eta_{0.02}^{0.29}T_{\rm
C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}
&, \text{cusp},
  \end{cases}
  \label{eq:vC2}
\end{align} 
Compton heating can thus be significant in young stellar populations with relatively high mass loss rates, e.g. $v_{w}^{\rm C} \gtrsim 300$ km s$^{-1}$ for $\eta \gtrsim 1$.  The mass accretion rate corresponding to the state where Compton heating limits the average accretion rate is given by substituting equation (\ref{eq:vC2}) into equation (\ref{eq:eddr_analytic}):
\begin{align}
\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
\begin{cases} 3\times 10^{-3} \eta_{0.02}^{0.20}T_{\rm
C,9}^{-0.8}\epsilon_{-2}^{-0.8} M_{\bullet,8}^{0.15}
&, \text{core}\\ 8\times 10^{-4} \eta_{0.02}^{0.30}T_{\rm
C,9}^{-0.7}\epsilon_{-2}^{-0.7} M_{\bullet,8}^{0.14}
&, \text{cusp},
  \end{cases}
  \label{eq:MdotCa}
\end{align}
If the accretion luminosity $\epsilon = 0.1 \dot{M}/\dot{M}_{\rm edd}$ depends on the Eddington ratio as predicted by some models for radiatively inefficient accretion flows (\citealt{Narayan&Yi95}; \citealt{Narayan+98}), then the Compton-limited accretion rate becomes
\begin{align}
\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
\begin{cases} 1.4\times 10^{-2} \eta_{0.02}^{0.11}T_{\rm
C,9}^{-0.44}M_{\bullet,8}^{0.08}
&, \text{core}\\ 6\times 10^{-3} \eta_{0.02}^{0.18}T_{\rm
C,9}^{-0.4} M_{\bullet,8}^{0.08}
&, \text{cusp}.
  \end{cases}
  \label{eq:MdotC}
\end{align}
{\bf AG: Note that I have included the bolometric correction for now.  BDM: are you doing everything consistently?}

>>>>

\begin{table*}
\begin{threeparttable}
%\centering
\begin{minipage}{18cm}
\caption{Summary of Numerical Solutions}
\begin{tabular}{lccccccccc}
  \hline
  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  $\Gamma$ &  $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.2}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.2}{\eta}\right)_{r_s}^{(d)}$}  \\
  ($M_{\odot}$) & (km s$^{-1}$) & (pc) &- & - & - &  & \\ 
\hline
 & & & Cusp Galaxies, $\Gamma^{(a)} = 0.8$ & & & & & \\
$    10^{ 6 }$ & 300 & 0.8 & 100 & 0.14 & $ 6.4 \times 10^{ -5 }$ & 17 \\
... & 600 & 0.8 & 100 & $ 3.4 \times 10^{ -2 }$ & $ 1.1 \times 10^{ -5 }$ & $ 1.6 \times 10^{ 3 }$ \\
... & 1200 & 0.8 & 100 & $ 8.2 \times 10^{ -3 }$ & $ 1.9 \times 10^{ -6 }$ & $ 7.2 \times 10^{ 4 }$ \\
$    10^{ 7 }$ & 300 & 0.8 & 25 & 0.65 & $ 3.9 \times 10^{ -4 }$ & 1.8 \\
... & ... & 0.8 & 50 & 0.65 & $ 3.9 \times 10^{ -4 }$ & $\mathbf{0.82}$ \\
... & ... & 0.8 & 100 & 0.83 & $ 5.2 \times 10^{ -4 }$ & $\mathbf{0.33}$ \\
... & ... & 0.8 & 200 & 0.91 & $ 5.9 \times 10^{ -4 }$ & $\mathbf{0.18}$ \\
... & ... & 0.8 & 400 & 2.3 & $ 1.8 \times 10^{ -3 }$ & $\mathbf{ 1.9 \times 10^{ -2 }}$ \\
... & 600 & 0.8 & 25 & $ 8.9 \times 10^{ -2 }$ & $ 3.6 \times 10^{ -5 }$ & $ 4.4 \times 10^{ 2 }$ \\
... & ... & 0.8 & 100 & $ 8.9 \times 10^{ -2 }$ & $ 3.6 \times 10^{ -5 }$ & $ 4.4 \times 10^{ 2 }$ \\
... & 1200 & 0.8 & 100 & $ 2.1 \times 10^{ -2 }$ & $ 6.4 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 4 }$ \\
$    10^{ 8 }$ & 300 & 0.8 & 25 & 1.3 & $ 9.4 \times 10^{ -4 }$ & $\mathbf{1}$ \\
... & ... & 0.8 & 50 & 2.1 & $ 1.6 \times 10^{ -3 }$ & $\mathbf{0.19}$ \\
... & ... & 0.8 & 100 & 3.8 & $ 3.3 \times 10^{ -3 }$ & $\mathbf{ 2.2 \times 10^{ -2 }}$ \\
... & ... & 0.8 & 200 & 7.3 & $ 7.2 \times 10^{ -3 }$ & $\mathbf{ 2.1
  \times 10^{ -3 }}$ \\
... & 450 & 0.8 & 100 & 0.72 & $ 4.4 \times 10^{ -4 }$ & 4 \\
...$^{\dagger}$ & ... & 0.8 & 100 & 3.3 & $ 2.8 \times 10^{ -3 }$ & $\mathbf{2.8}$\\
... & 600 & 0.8 & 25 & 0.26 & $ 1.3 \times 10^{ -4 }$ & $ 1.1 \times 10^{ 2 }$ \\
... & ... & 0.8 & 100 & 0.28 & $ 1.5 \times 10^{ -4 }$ & 76 \\
...$^{\dagger}$ & ... & 0.8 & 100 & 0.29 & $ 1.5 \times 10^{ -4 }$ & 70 \\
... & ... & 0.8 & 200 & 0.3 & $ 1.5 \times 10^{ -4 }$ & 67 \\
... & ... & 0.8 & 400 & 0.31 & $ 1.6 \times 10^{ -4 }$ & 58 \\
... & 1200 & 0.8 & 100 & $ 5.4 \times 10^{ -2 }$ & $ 2.0 \times 10^{
  -5 }$ & $ 7.2 \times 10^{ 3 }$ \\
  \hline
 & & & Core Galaxies, $\Gamma = 0.1$ & & & & & & \\
$    10^{ 6 }$ & 600 & 0.1 & 25 & $ 9.9 \times 10^{ -2 }$ & $ 8.2 \times 10^{ -6 }$ & 99 \\
... & ... & 0.1 & 50 & 0.34 & $ 8.5 \times 10^{ -5 }$ & $\mathbf{0.45}$ \\
... & 1200 & 0.1 & 25 & $ 1.7 \times 10^{ -2 }$ & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
... & ... & 0.1 & 50 & $ 1.7 \times 10^{ -2 }$ & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
... & ... & 0.1 & 100 & $ 1.7 \times 10^{ -2 }$ & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
$    10^{ 7 }$ & 600 & 0.1 & 25 & 0.24 & $ 4.3 \times 10^{ -5 }$ & 41 \\
... & ... & 0.1 & 50 & 0.57 & $ 2.3 \times 10^{ -4 }$ & $\mathbf{0.38}$ \\
... & 1200 & 0.1 & 25 & $ 4.4 \times 10^{ -2 }$ & $ 1.8 \times 10^{ -6 }$ & $ 2.2 \times 10^{ 4 }$ \\
... & ... & 0.1 & 50 & $ 4.7 \times 10^{ -2 }$ & $ 2.0 \times 10^{ -6 }$ & $ 1.7 \times 10^{ 4 }$ \\
... & ... & 0.1 & 100 & $ 5.3 \times 10^{ -2 }$ & $ 2.5 \times 10^{ -6 }$ & $ 9.8 \times 10^{ 3 }$ \\
$    10^{ 8 }$ & 600 & 0.1 & 25 & 0.39 & $ 1.1 \times 10^{ -4 }$ & 31 \\
... & ... & 0.1 & 50 & 0.66 & $ 3.0 \times 10^{ -4 }$ & 3 \\
... & ... & 0.1 & 100 & 2.6 & $ 4.0 \times 10^{ -3 }$ & $\mathbf{ 5.7 \times 10^{ -3 }}$ \\
... & 1200 & 0.1 & 25 & 0.1 & $ 8.4 \times 10^{ -6 }$ & $ 5.6 \times 10^{ 3 }$ \\
... & ... & 0.1 & 50 & 0.11 & $ 9.8 \times 10^{ -6 }$ & $ 4.0 \times 10^{ 3 }$ \\
... & ... & 0.1 & 100 & 0.12 & $ 1.2 \times 10^{ -5 }$ & $ 2.4 \times 10^{ 3 }$ \\
... & ... & 0.1 & 200 & 0.16 & $ 2.1 \times 10^{ -5 }$ & $ 6.5 \times 10^{ 2 }$ \\
... & ... & 0.1 & 400 & 3.3 & $ 6.2 \times 10^{ -3 }$ & $\mathbf{ 5.8 \times 10^{ -3 }}$ \\
  \hline

@@

If Compton heating acts alone, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then solving equation
(\ref{eq:vC}) for $\tilde{v}_{\rm w}$ yields
\begin{align} v_{w}^{\rm C} \simeq
  \begin{cases} 150 \eta_{0.02}^{0.21}T_{\rm
C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}
&, \text{core}\\ 96 \eta_{0.02}^{0.29}T_{\rm
C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}
&, \text{cusp},
  \end{cases}
  \label{eq:vC2}
\end{align} 
Compton heating can thus be significant in young stellar populations with relatively high mass loss rates, e.g. $v_{w}^{\rm C} \gtrsim 300$ km s$^{-1}$ for $\eta \gtrsim 1$.  The mass accretion rate corresponding to the state where Compton heating limits the average accretion rate is given by substituting equation (\ref{eq:vC2}) into equation (\ref{eq:eddr_analytic}):
\begin{align}
\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
\begin{cases} 3\times 10^{-3} \eta_{0.02}^{0.20}T_{\rm
C,9}^{-0.8}\epsilon_{-2}^{-0.8} M_{\bullet,8}^{0.15}
&, \text{core}\\ 8\times 10^{-4} \eta_{0.02}^{0.30}T_{\rm
C,9}^{-0.7}\epsilon_{-2}^{-0.7} M_{\bullet,8}^{0.14}
&, \text{cusp},
  \end{cases}
  \label{eq:MdotCa}
\end{align}
If the accretion luminosity $\epsilon = 10 \dot{M}/\dot{M}_{\rm edd}$
depends on the Eddington ratio as predicted by some models for
radiatively inefficient accretion flows (\citealt{Narayan&Yi95};
\citealt{Narayan+98}; \citealt{XieYuan:2012a}), then the Compton-limited accretion rate becomes
\begin{align}
\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
\begin{cases} 1.8\times 10^{-2} \eta_{0.02}^{0.11}T_{\rm
C,9}^{-0.44}M_{\bullet,8}^{0.08}
&, \text{core}\\ 8.7\times 10^{-4} \eta_{0.02}^{0.17}T_{\rm
C,9}^{-0.4} M_{\bullet,8}^{0.08}
&, \text{cusp}.
  \end{cases}
  \label{eq:MdotC}
\end{align}
{\bf  Total efficiency is 10 (mdot/MdotEdd). Everywhere.}
